MSDS 6306: Doing Data Science - Case Study 01 - Beers/Breweries Dataset

### 2020-10-24 MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd
Update MSDS6306_DDS_CaseStudy01-Beersdataset.Rmd
Rmd file

```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyr)
require(graphics)
library(tidyverse)
library(magrittr)
library(GGally)
library(ggthemes)
library(plotly)
library(maps)
library(stringr)
library(stringi)
library(mapproj)
library(RCurl)
library(readr)
library(rio)

#Beer and Breweries data input from CSV files
```{r Beer Data}
# This reads in the Beers data from select folder file Beers.csv.
Beerdata <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Beers.csv",header = T,sep = ",",na.strings = "NA",fill = TRUE);
head(Beerdata)
nrow(Beerdata)
```

```{r Brewery Data}
# This reads in the Beers data from select folder file Breweries.csv.
Breweriesdata <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Breweries.csv",header = T,sep = ",",na.strings = "NA",
                          fill = TRUE);
head(Breweriesdata)
nrow(Breweriesdata)
```

# Generating bar plots for Beerdata categorized by number of Ounces used to generate ABV
```{r Plots}
#Removing not applicable ABV values
Beerdata1 <- Beerdata %>% filter(Beerdata$ABV != "NA") 
Beerdata1$Ounces <- as.factor(Beerdata1$Ounces)

#Summary count of number of ABV values by categorized Ounces of beer
s <- Beerdata1 %>% group_by(Ounces)%>% summarize(ABV,count=n())

# Bar plot of ABV v. Ounces to see how much data is available
Beerdata1 %>% ggplot(aes(x = Ounces, y = s$count[1], fill=Ounces)) + geom_col() +
  ggtitle("Alcohol By Volume (ABV) data count by Ounce Category") +
  labs(y="Alcohol By Volume (ABV)") + 
  geom_text(aes(Ounces, s$count+100, label = s$count, fill = NULL), data = s)
```

#Generating geographic plots from breweries data
```{r mapdata Breweries}
#makes a data frame with State name and abbreviation.
lookup = data.frame(abb = state.abb, State = state.name)
dc <- c("DC", "District of Columbia")
lookup <- rbind(lookup,dc)
# Change Column Name State to abb (abbreviation)
colnames(Breweriesdata)[4] = "abb"

@@

#Code below adds scaled legend to the Breweries count by state
cplot <- Nplot + theme(legend.background = element_rect(fill="gray90", size=10, linetype="dotted"),legend.key.height = unit(4,"lines"))

#final plot with state names and Breweries count by state
cplot

```
#Merging beer data and breweries data
```{r merging beer and breweries data}

@@

>>>>

#R libraries
```{r libraries}
library(knitr)
library(yaml)
library(dplyr)
library(ggplot2)
library(tidyr)
require(graphics)
library(tidyverse)
library(magrittr)
library(GGally)
library(ggthemes)
library(plotly)
library(maps)
library(stringr)
library(stringi)
library(mapproj)
library(RCurl)
library(readr)
library(rio)
library(naniar)
library(scales)
library(grid)
library(mice)
library(class)
library(caret)
library(e1071)
library(datasets)
```

#Beer and Breweries data input from CSV files
```{r Beer Data}
# This reads in the Beers data from select folder file Beers.csv.
Beerdata <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Beers.csv",
                     header = T,sep = ",",na.strings = "NA",fill = TRUE)
head(Beerdata)
```
#Number of rows in Beer data
```{r number of beer data}
nrow(Beerdata)
```

```{r Brewery Data}
# This reads in the Beers data from select folder file Breweries.csv.
Breweriesdata <- read.csv("https://raw.githubusercontent.com/VenkataVanga/MSDS-6306/main/Breweries.csv",
                          header = T,sep = ",",na.strings = "NA", fill = TRUE)
head(Breweriesdata)
```

#Number of rows in Breweries data
```{r number of breweries data}
nrow(Breweriesdata)
```

#Generating geographic plots from breweries data (following chunk generate the final plot)
```{r mapdata Breweries}
#makes a data frame with State name and abbreviation.
lookup = data.frame(abb = state.abb, State = state.name)
dc <- c("DC", "District of Columbia")
lookup <- rbind(lookup,dc)
# Change Column Name State to abb (abbreviation)
colnames(Breweriesdata)[4] = "abb"

@@

#Code below adds scaled legend to the Breweries count by state
cplot <- Nplot + theme(legend.background = element_rect(fill="gray90", 
                                                        size=10, linetype="dotted"),
                       legend.key.height = unit(4,"lines")) + 
  theme(plot.title = element_text(size=14, face= "bold", colour= "black"))
```

#Final plot with state names and Breweries count by state
```{r map breweries, fig.width=35, fig.height=20, dpi = 240}
cplot  #plot best viewed in scaled full screen zoom 1920px x 1080px (21" or higher dim screen)
```
The final plot shows that 'Colorado' has the highest (47)number of breweries followed by 'California (39)', 'Michigan(32)' and 'Oregon(29)' being the next three successors.

#Merging beer data and breweries data
```{r merging beer and breweries data}
colnames(Beerdata)[5] = "Brew_ID" #Changing columun name to combine both beer data and breweries data
Totaldata <- merge(Beerdata,Breweriesdata, by="Brew_ID", all.x = T) %>% na_if("")
colnames(Totaldata)[2] = "Beer_Name" #Changing the column name to Beer name
colnames(Totaldata)[8] = "Brewery_Name" # Changing the column name to Brewery name
colnames(Totaldata)[10] = "State" # Changing the column name back to State

@@

#First 6 observations after merging beer data and breweries data
```{r First 6 observations after merging}
head(Totaldata,6)
```

#Last 6 observations after merging beer data and breweries data
```{r Last 6 observations after merging}
tail(Totaldata,6)
```

#Missing Values in ABV/IBU columns
```{r Missing Values in ABV/IBU columns}
table(is.na(Totaldata$ABV)) # True value represents NA values in the column ABV in original data
table(is.na(Totaldata$IBU)) # True value represents NA values in the column IBU in original data
table(is.na(Totaldata$Style)) # True value represents NA values in the column Style in original data
gg_miss_var(Totaldata)+ ggtitle("Missing data values by Category")+scale_y_log10() + theme(
# AXIS LABLES APPEARANCE
plot.title = element_text(size=14, face= "bold", colour= "black" ),
axis.title.x = element_text(size=12, face="bold", colour = "black"),    
axis.title.y = element_text(size=12, face="bold", colour = "black"),    
axis.text.x = element_text(size=12, face="bold", colour = "black"), 
axis.text.y = element_text(size=12, face="bold", colour = "black"),
strip.text.x = element_text(size = 10, face="bold", colour = "black" ),
strip.text.y = element_text(size = 10, face="bold", colour = "black"),
)
```

The plot and the values in tables above provide the missing data values in ABV (65), IBU (1005) and Style (5) columns from originally considered beer data.

#Addressing the missing values
```{r, Addressing missing values}
#MICE - Multivariate Imputation by Chained Equations method is used to impute the missing variables in ABV and IBU columns
imp <- mice(Totaldata, method='norm.predict', m=5)
Totaldata_imp=complete(imp)
gg_miss_var(Totaldata_imp) # shows only style as missing data
table(is.na(Totaldata_imp$Style)) # True value represents NA values in the column Style in original data
Totaldata_imp[c(which(is.na(Totaldata_imp$Style))),]
#Internet search for all the missing styles above
Totaldata_imp[227,"Style"] = "English India Pale Ale (IPA)" #"https://irp-cdn.multiscreensite.com/b5112d09/files/uploaded/Beer%20Menu_2up%20%281%29-1.png"

Totaldata_imp[455,"Style"] = "Vienna Lager"  #https://www.craftbeer.com/styles/german-style-marzen-oktoberfest#:~:text=A%20beer%20rich%20in%20malt,similar%20to%20the%20Vienna%20lager.&text=Originating%20in%20Germany%2C%20this%20style,or%20lagered%2C%20throughout%20the%20summer.

Totaldata_imp[946,"Style"] = "Scotch Ale / Wee Heavy"  #based on name

Totaldata_imp[992,"Style"] = "German Pilsener" #https://www.oskarblues.com/beers/

Totaldata_imp[993,"Style"] = "German Pilsener" #https://www.oskarblues.com/beers/

```
# Generating bar plots for Beerdata categorized by number of Ounces used to generate ABV
```{r ABV by ounces}
Totaldata_imp$Ounces <- as.factor(Totaldata_imp$Ounces)

#Summary count of number of ABV values by categorized Ounces of beer
s <- Totaldata_imp %>% group_by(Ounces)%>% summarize(ABV,count=n())

# Bar plot of ABV v. Ounces to see how much data is available
Totaldata_imp %>% ggplot(aes(x = Ounces, y = s$count[1], fill=Ounces)) + geom_col() +
  ggtitle("Alcohol By Volume (ABV) data count by Ounce Category") +
  labs(y="Alcohol By Volume (ABV)") + 
  geom_text(aes(Ounces, s$count+50, label = s$count, fill = NULL), data = s)
```

#Median for ABV and IBU content for each state (final plot given in below chunk)
```{r Median ABV and IBU content for each state}
#Evaluating median of ABV and IBU (all NA values removed from data)
Median_ABV <- Totaldata_imp %>% arrange(State) %>% group_by(State) %>% 
  summarize(Median_ABV = median(ABV, na.rm = TRUE))
Median_IBU <- Totaldata_imp %>% arrange(State) %>% group_by(State) %>% 
  summarize(Median_IBU = median(IBU, na.rm = TRUE))
Median_ABV <- data.frame(Median_ABV)
Median_IBU <- data.frame(Median_IBU)
Median_ABV$Cat <- "Median_ABV"
Median_IBU$Cat <- "Median_IBU"

#Bar plot for Median ABV/IBU content for each state
Medianplot_ABV_IBU <- Median_ABV %>% ggplot(mapping = aes(x,y)) + 
  geom_bar(aes(x = State, y = Median_ABV, fill = State), group = Median_ABV$State, 
                                                   stat = 'identity', show.legend = FALSE) +
  ggtitle('Median ABV Content by State') + geom_text(aes(State, Median_ABV+0.005, 
                                                      label = percent(Median_ABV, accuracy = 0.01),
                                                      fill = NULL), data = Median_ABV, angle = 90) + 
  geom_bar(data=Median_IBU, aes(x = State, y = Median_IBU, fill = State), stat = 'identity', 
           show.legend = FALSE) +
  geom_text(aes(State, Median_IBU+2, label = round(Median_IBU,digits = 0), fill = NULL), data = Median_IBU) +
  ggtitle('Median ABV and Median IBU Content by State') + facet_grid(Cat~., scale = "free_y",
                                                              labeller = label_parsed, switch = "y") + labs(x="State") + 
  theme(axis.title.y = element_blank(), strip.placement = "outside",axis.title.x = element_text(size=12, face="bold", colour = "black"),    
axis.text.x = element_text(size=12, face="bold", colour = "black"), 
axis.text.y = element_text(size=12, face="bold", colour = "black"),
strip.text.x = element_text(size = 10, face="bold", colour = "black" ),
strip.text.y = element_text(size = 10, face="bold", colour = "black"),
)

# Median plot for ABV and IBU by state
```{r Final Median Plot for ABV and IBU by state,fig.width=30, fig.height=15, dpi = 240}
Medianplot_ABV_IBU 
#plot best viewed in scaled full screen zoom 1920px x 1080px (21" or higher dim screen)
```

From the median ABV and median IBU plot above it can be observed that 'District of Columbia' and 'Kentucky' have the highest median ABV values shown in percentage. 
'Maine' and 'West Virginia' have the highest median IBU values.

# Maximum ABV and IBU by State
```{r maximum ABV and IBU State}
#collecting max data
Max_ABV <- Totaldata_imp %>% arrange(State) %>% group_by(State) %>% 
  summarize(Max_ABV = max(ABV, na.rm=TRUE))
Max_IBU <- Totaldata_imp %>% arrange(State) %>% group_by(State) %>% 
  summarize(Max_IBU = max(IBU, na.rm=TRUE))

Max_ABV$Cat <- "Max_ABV"
Max_IBU$Cat <- "Max_IBU"

#Bar plot for max ABV content for each state
Maxplot_ABV_IBU <- Max_ABV %>% ggplot(mapping = aes(x,y)) + 
  geom_bar(aes(x = State, y = Max_ABV, fill = State), group = Max_ABV$State, 
                                                   stat = 'identity', show.legend = FALSE) +
  ggtitle('Max ABV Content by State') + geom_text(aes(State, Max_ABV+0.0085, 
                                                      label = percent(Max_ABV, accuracy = 0.01),
                                                      fill = NULL), data = Max_ABV, angle = 90) + 
  geom_bar(data=Max_IBU, aes(x = State, y = Max_IBU, fill = State), stat = 'identity', 
           show.legend = FALSE) +
  geom_text(aes(State, Max_IBU+5, label = round(Max_IBU,digits = 0), fill = NULL), data = Max_IBU) +
  ggtitle('Max ABV and Max IBU Content by State') + facet_grid(Cat~., scale = "free_y",
                                                              labeller = label_parsed, switch = "y") + labs(x="State") + 
  theme(axis.title.y = element_blank(), strip.placement = "outside",axis.title.x = element_text(size=12, face="bold", colour = "black"),    
axis.text.x = element_text(size=12, face="bold", colour = "black"), 
axis.text.y = element_text(size=12, face="bold", colour = "black"),
strip.text.x = element_text(size = 10, face="bold", colour = "black" ),
strip.text.y = element_text(size = 10, face="bold", colour = "black"),
)

# Maximum ABV and IBU vaule by state
```{r Final Max ABV and IBU by state,fig.width=30, fig.height=20, dpi = 240}
Maxplot_ABV_IBU 
#plot best viewed in scaled full screen zoom 1920px x 1080px (21" or higher dim screen)
```

From the Max ABV and IBU plot it is observed that 'Colorado' has the max ABV value of 12.8% and 'Oregon' has the max IBU value of 138.

# ABV statistical attributes
```{r ABV statistical attributes}
Stats <- Totaldata_imp %>% summarize(Mean = mean(ABV, na.rm=TRUE),
                        Median = median(ABV,na.rm=T), Max = max(ABV,na.rm=T), Min = min(ABV,na.rm=T),
                        SD = sd(ABV,na.rm=T), N = n())
#Histogram and Density Plot
His_Den <- Totaldata_imp %>% filter(!is.na(ABV)) %>% ggplot(aes(x=ABV)) +
  geom_histogram(aes(y=..density..),colour='red',fill='blue', binwidth = 0.0035) +
  geom_density(alpha=.4, fill='#FFFF00') + 
  ggtitle('ABV Statistical Attributes - Histogram, Density and Box Plots') + 
  scale_x_continuous(breaks = seq(0,0.14,0.01),labels = seq(0,0.14,0.01)) + labs(y="Density / Count")

#Box plot for ABV data
Box <- Totaldata_imp %>% filter(!is.na(ABV)) %>% ggplot(aes(x=ABV)) + 
  geom_boxplot(col='black',fill='#FF6666') + scale_x_continuous(expand = c(0,0), limit = c(0,0.14)) + scale_y_continuous(expand = c(0,0), limit = c(-0.4,0.4))

#Histogram density plot and Box plot on same scale
grid.draw(rbind(ggplotGrob(His_Den),
                ggplotGrob(Box),
                size = "first"))
Stats
```
All statistically significant attributes for the ABV values are shown above
The distribution of ABV is slightly right skewed. 
ABV values from 4.90% to 5.95% are the most widely used.
6.5% ABV values show second highest peak from the histogram.
. 
There are total 2410 non-missing ABV values in this data set. 
The maximum ABV is 12.8%, the minimum ABV is .1%.
The mean ABV is 5.98%, median 5.7% and standard deviation of ABV is 1.34%.

# ABV v. IBU scatter plot
```{r ABV v. IBU}
#Scatter plot with 
Totaldata_imp %>% filter(!is.na(ABV) & !is.na(IBU)) %>% 
  ggplot(aes(y=ABV, x=IBU)) + geom_point(aes(colour = ABV/IBU)) + geom_smooth(method=loess) + ggtitle("ABV V. IBU Plot") + scale_y_continuous(labels = percent)
```

The scatter plot indicates there is a moderately positive linear relationship (i.e., as IBU increases ABV increases).
Most beers with lower IBU (less than 50) have ABV values around 5%.
When IBU value increases, ABV values spreads out. But most beers with IBU values above 50, their ABV values spread out within the region between 5% and 10%.

# ABV_IBU statistical significance with respect to IPAs and Ale's 
```{r, ABV-IBU with respect to IPAs and Ale}
# ABV/ IBU for IPA
Data_IPA <- Totaldata_imp %>% 
  filter(str_detect(Style, regex(str_c('\\b','IPA','\\b',sep=''), ignore_case = T)))
#Stats IPA
Stats_IPA_ABV <- Data_IPA %>% summarize(Mean = mean(ABV, na.rm=TRUE),
                        Median = median(ABV,na.rm=T), Max = max(ABV,na.rm=T), Min = min(ABV,na.rm=T),
                        SD = sd(ABV,na.rm=T), N = n())
Stats_IPA_IBU <- Data_IPA %>% summarize(Mean = mean(IBU, na.rm=TRUE),
                        Median = median(IBU,na.rm=T), Max = max(IBU,na.rm=T), Min = min(IBU,na.rm=T),
                        SD = sd(IBU,na.rm=T), N = n())
#Histogram and Density Plot for IPA with ABV
His_Den_IPA_ABV <- Data_IPA %>% ggplot(aes(x=ABV)) +
  geom_histogram(aes(y=..density..),colour='red',fill='blue', binwidth = 0.0035) +
  geom_density(alpha=.4, fill='#FFFF00') + 
  ggtitle('IPA - ABV Statistical Attributes - Histogram, Density') + 
  scale_x_continuous(breaks = seq(0,0.14,0.01),labels = seq(0,0.14,0.01)) + labs(y="Density / Count")
#Histogram and Density Plot for IPA with IBU
His_Den_IPA_IBU <- Data_IPA %>% ggplot(aes(x=IBU)) +
  geom_histogram(aes(y=..density..),colour='red',fill='pink') +
  geom_density(alpha=.2, fill='#FFFF00') + 
  ggtitle('IPA - IBU Statistical Attributes - Histogram, Density') + 
  scale_x_continuous() + labs(y="Density / Count")

#ABV / IBU for Ale
Data_Ale <- Totaldata_imp %>% 
  filter(str_detect(Style, regex(str_c('\\b','Ale','\\b',sep=''), ignore_case = T)))

Stats_Ale_ABV <- Data_Ale %>% summarize(Mean = mean(ABV, na.rm=TRUE),
                        Median = median(ABV,na.rm=T), Max = max(ABV,na.rm=T), Min = min(ABV,na.rm=T),
                        SD = sd(ABV,na.rm=T), N = n())
Stats_Ale_IBU <- Data_Ale %>% summarize(Mean = mean(IBU, na.rm=TRUE),
                        Median = median(IBU,na.rm=T), Max = max(IBU,na.rm=T), Min = min(IBU,na.rm=T),
                        SD = sd(IBU,na.rm=T), N = n())
#Histogram and Density Plot for Ale with ABV
His_Den_Ale_ABV <- Data_Ale %>% ggplot(aes(x=ABV)) +
  geom_histogram(aes(y=..density..),colour='red',fill='blue', binwidth = 0.0035) +
  geom_density(alpha=.4, fill='#FFFF00') + 
  ggtitle('Ale - ABV Statistical Attributes - Histogram, Density') + 
  scale_x_continuous(breaks = seq(0,0.19,0.01),labels = seq(0,0.19,0.01)) + labs(y="Density / Count")
#Histogram and Density Plot for Ale with IBU
His_Den_Ale_IBU <- Data_Ale %>% ggplot(aes(x=IBU)) +
  geom_histogram(aes(y=..density..),colour='red',fill='pink') +
  geom_density(alpha=.2, fill='#FFFF00') + 
  ggtitle('Ale - IBU Statistical Attributes - Histogram, Density') + 
  scale_x_continuous() + labs(y="Density / Count")

#Fitting all the statistical data in one screen
require(gridExtra)
a <- grid.arrange(His_Den_IPA_ABV,His_Den_IPA_IBU,His_Den_Ale_ABV,His_Den_Ale_IBU,ncol=2)
Stats_IPA_ABV
Stats_IPA_IBU
Stats_Ale_ABV
Stats_Ale_IBU
```

The above plots and values show IPA's have higher ABV and IBU values than the Ale's. This indicates that IPA's are more alcoholic and more bitter than the Ale's in general.

#ABV_IBU with respect to IPAs and Ale's using kNN
```{r, ABV_IBU with respect to IPAs and Ale using kNN}
#Checking to see number of rows in each IPA and Ale data
nrow(Data_IPA)
nrow(Data_Ale)

Data_IPA$Style1 <- "IPA" #Adding Style1 column for IPA style beer as IPA
Data_Ale$Style1 <- "Ale" #Adding Style1 column for Ale style beer as Ale
Data_IPA$Style1 <- as.factor(Data_IPA$Style1)
Data_Ale$Style1 <- as.factor(Data_Ale$Style1)

#Combining the IPA and Ale data to create a training set
Data_Ale_IPA <- rbind(Data_IPA, Data_Ale)

#Plot of all IPA and Ale data
Data_Ale_IPA %>% ggplot(aes(x=IBU, y=ABV)) + geom_point(aes(colour=Style1)) +
  theme(axis.title.x = element_text(size=12, face="bold", colour = "black"),    
axis.text.x = element_text(size=12, face="bold", colour = "black"),
axis.title.y = element_text(size=12, face="bold", colour = "black"),
axis.text.y = element_text(size=12, face="bold", colour = "black"),
strip.text.x = element_text(size = 10, face="bold", colour = "black" ),
strip.text.y = element_text(size = 10, face="bold", colour = "black"),
) + ggtitle("ABV v. IBU based on Style") + labs(colour = "Style")

# kNN approach for 500 dataset iterations and 1-30 k values
iterations = 500 # number of iterations to test the k value
numks = 30      # number of k used in the iterations
splitPerc = .7 # split percentage assumed from the total dataset
masterAcc = matrix(nrow = iterations, ncol = numks)
set.seed(6)
trainIndices = sample(1:dim(Data_Ale_IPA)[1],round(splitPerc * dim(Data_Ale_IPA)[1]))
beer_train = Data_Ale_IPA[trainIndices,]
beer_test = Data_Ale_IPA[-trainIndices,]
#columns 4 and 5 represent the ABV and IBU values 
classifications = knn(beer_train[,c(4,5)],beer_test[,c(4,5)],beer_train$Style1, prob = TRUE, k = 5)
CM = confusionMatrix(table(classifications,beer_test$Style1))
classifications
CM
#Above Confusion Matrix and Statistics show a accuracy of ~80%
for(j in 1:iterations)
{
  accs = data.frame(accuracy = numeric(30), k = numeric(30))
  trainIndices = sample(1:dim(Data_Ale_IPA)[1],round(splitPerc * dim(Data_Ale_IPA)[1]))
  beer_train = Data_Ale_IPA[trainIndices,]
  beer_test = Data_Ale_IPA[-trainIndices,]
  for(i in 1:numks)
  {
    classifications = knn(beer_train[,c(4,5)],beer_test[,c(4,5)],beer_train$Style1, prob = TRUE, k = i)
    table(classifications,beer_test$Style1)
    CM = confusionMatrix(table(classifications,beer_test$Style1))
    masterAcc[j,i] = CM$overall[1]
  }
}
MeanAcc = colMeans(masterAcc)
p = ggplot(mapping = aes(x = seq(1,numks,1), y = MeanAcc)) + geom_line() + ggtitle("Mean Accuracy v. Number of k") + xlab('k values')
ggplotly(p)
```

Considering the IPA and Ale data using 70%/30% split and shuffling test and training data 500 times, with K assigned from 1 to 30 during each shuffling, we can achieve the highest mean accuracy 80.0% when K=5.

# ABV_IBU with respect to IPAs and Ale's using Naive Bayes
```{r, ABV_IBU with respect to IPAs and Ale using Naive Bayes}
iterations = 500
masterAcc = matrix(nrow = iterations)
masterSen = matrix(nrow = iterations)
masterSpec = matrix(nrow = iterations)
splitPerc = .7 
for(j in 1:iterations)
{

  trainIndices = sample(1:dim(Data_Ale_IPA)[1],round(splitPerc * dim(Data_Ale_IPA)[1]))
  beer_train = Data_Ale_IPA[trainIndices,]
  beer_test = Data_Ale_IPA[-trainIndices,]
  model = naiveBayes(beer_train[,c(4,5)],as.factor(beer_train$Style1),laplace = 1)
  table(predict(model,beer_test[,c(4,5)]),as.factor(beer_test$Style1))
  CM = confusionMatrix(table(predict(model,beer_test[,c(4,5)]),as.factor(beer_test$Style1)))
  masterAcc[j] = CM$overall[1]
  masterSen[j] = CM$byClass[1]
  masterSpec[j] = CM$byClass[2]
}
MeanAcc = colMeans(masterAcc)
MeanSen = colMeans(masterSen)
MeanSpec = colMeans(masterSpec)
MeanAcc
MeanSen
MeanSpec
```

Naive Bayes model run for 500 iterations and 70/30% split gave the Mean accuracy (~79%), Mean sensitivity (~67%) and Mean specificity (~86%) as shown from the values above. The data is close match with kNN model.

Please go through the presentation final conclusion for the entire data.
